Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Wording
Grammar

BDD includes TDD, amongst other software development methodologies,
but with a terminology and mindset shifted towards
specification instead of testing.
In BDD, specifications can be used for
automated testing.
BDD is meant to be an enjoyable experience for the developer.
Compared to TDD it provides a much nicer syntax that
makes tests very easy to read.  And like TDD it puts emphasis on
test automation, to take work load from the shoulders of
developers.
BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

@@

We will show how to use Doctest and Hspec in combination, to design,
document and test Haskell code.
Both, Doctest and Hspec are missing some features.  So we extend them
as needed.  In particular, our contributions are:

>>>>

BDD includes TDD, amongst other software development methodologies,
but with a terminology and mindset shifted towards
specification instead of testing.
In BDD, specifications can be used for
automated testing.
BDD is meant to be an enjoyable experience for the developer.
Compared to TDD it provides a much nicer syntax that
makes tests very easy to read.  And like TDD it puts emphasis on
test automation, to take workload off the shoulders of
developers.
BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

@@

We will show how to use Doctest and Hspec in combination, to design,
document and test Haskell code.
Both, Doctest and Hspec were missing some features.  So we extended
them as needed.  In particular, our contributions are:
